TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2016-12-22 ISORC2017/paper.tex
Update variously

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Takuro Yamamoto}
\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and
\IEEEauthorblockN{Takuma Hara}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Ishikawa}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Hiroshi Oyama}
\IEEEauthorblockA{OKUMA Corporation}
\and
\IEEEauthorblockN{Hiroaki Takada}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Azumi}
\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

@@

Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.

TINET is a TCP/IP protocol stack for embedded systems.
TINET is a compact TCP/IP protocol stack, however consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.

To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and add/remove TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET, and confirm that the overheads of execution time and memory consumption are low and  that the configurability is improved.

@@

Internet of Things (IoT) is an essential keyword for the next era.
Such as wearable devices, smart devices, and smart homes, various things are connected to the Internet, enriching our lives.
Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
Therefore, embedded network software is required for the high productivity and quality.

TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual Component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, that component behaviors and interconnections are defined statically, thus TECS can optimize the overhead of componentization.

@@

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:Basic Technology} introduces the basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation and Demonstration} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\section{Basic Technology}
\label{sec:Basic Technology}

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
TINET has been released as open source.

Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
    \caption{Hierarchy Diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINET_Hier}
\end{figure}

@@

\subsection{send, receive specifier}

TECS supports send and receive specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses send and receive specifiers instead of in and out to reduce the number of copies.

in is a specifier for input arguments.
A callee side uses the memory of arguments with in while executing the callee function.
When the processing returns to the caller side, the caller can reuse and deallocate the memory.

send is also a specifier for transferring data to a callee from a caller such as in.
The difference between in and send is whether to deallocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
In case of in specifier, both allocating and deallocating the data memory are performed in the caller.
On the other hand, in case of send, the caller allocates the data memory and the callee deallocates it.

out is a specifier for output arguments.
A callee writes data in the memory allocated by a caller, and the caller receives the data.

receive is also a specifier for a caller receiving data from a callee such as out.
The difference between out and receive is whether to allocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
While, in case of out, a callee writes data in the memory allocated by a caller, in case of receive, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

@@

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Takuro Yamamoto}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
\and
\IEEEauthorblockN{Takuma Hara}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Ishikawa}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Hiroshi Oyama}
\IEEEauthorblockA{OKUMA Corporation}
\and
\IEEEauthorblockN{Hiroaki Takada}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Azumi}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
}

@@

Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
TINET is a TCP/IP protocol stack for embedded systems.
Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.

To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET.
We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.

@@

Internet of Things (IoT) is an essential keyword for the next era.
Such as wearable devices, smart devices, and smart homes, various things are connected to the Internet, enriching our lives.
Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
It is not practical to implement the same communication function as a general computer because embedded systems have several restrictions such as low memory capacity.

TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs only small memory for its TCP/IP protocol stack; therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
In other words, TINET is composed of many files and defines many macros.
This may take a lot of time for software developers to maintain, extend, and analysis the software.
Embedded network software is required for the high productivity and quality.

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.

@@

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation and Demonstration} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\section{System Model}
\label{sec:System Model}

This section describes system model, including the basic technologies such as TINET and TECS.
System model of the proposed system is shown as Fig. \ref{fig:System Model}.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
    \caption{System model}
    \label{fig:SystemModel}
\end{figure}

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
TINET has been released as open source.

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.

To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINET_Hier}
\end{figure}

@@

\subsection{Component of protocol stack}

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

\subsection{send/receive specifier}

TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.

{\it in} is a specifier for input arguments.
A callee side uses the memory of arguments with {\it in} during executing the callee function.
When the processing returns to the caller side, the caller can reuse and deallocate the memory.

{\it send} is also a specifier for transferring data to a callee from a caller such as {\it in}.
The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
In case of {\it in} specifier, both allocating and deallocating the data memory are performed in the caller.
On the other hand, in case of {\it send}, the caller allocates the data memory and the callee deallocates it.

{\it out} is a specifier for output arguments.
A callee writes data in the memory allocated by a caller, and the caller receives the data.

{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

@@

Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}.

{\bf uIP:}
uIP (microIP) is a very small TCP/IP stack intended for tiny 8-bit and 16-bit microcontrollers.
uIP only requires about five kilobytes of code size and several hundred bytes of RAM.
uIP has been ported to various systems and has found its way into many commercial products.
After ver. 1.0 is released, later versions of uIP, including uIPv6, are integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontroller to the Internet.

{\bf lwIP:}
lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems.
The focus of lwIP is to reduce memory resource while still having a full scale TCP.
lwIP requires about 40 kilobytes of ROM and tens of kilobytes of RAM.
lwIP is larger than uIP, but provides better throughput.

{\bf CiAO/IP:}
